Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
think I may have finished first pass at goodness-of-fit section

Thus, our degree-resolution goodness-of-fit analysis has generally confirmed
the conclusions of $\S$\ref{sec:global}. We find the single-MBB $\beta$ value 
favored by the combination of \PLANCK~and DIRBE to be nearly identical here 
($\beta$=1.57) versus in $\S$\ref{sec:global}. As in $\S$\ref{sec:global}, we 
also find that the \PLANCK+FIRAS and\PLANCK+DIRBE best-fit two-component models
from Table \ref{tab:global} outperform single-MBB alternatives, though only by 
a relatively small margin. The agreement between our correlation slope analysis
and the present goodness-of-fit analysis is especially encouraging for two main
reasons: (1) in the present analysis, dust temperature was allowed to vary on 
degree scales, whereas in $\S$\ref{sec:global} we assumed a single global dust 
temperature (2)

% end with a few sentences summarizing overall takeaway(s) from this 
% goodness-of-fit analysis

@@

% also should emphasize that an important difference here relative to the
% correlation slope analysis is that here, the zero levels actually do matter

>>>>

Thus, our degree-resolution goodness-of-fit analysis has generally confirmed
the conclusions of $\S$\ref{sec:global}. We find the single-MBB $\beta$ value 
favored by the combination of \PLANCK~and DIRBE to be nearly identical here 
($\beta$=1.57) versus in $\S$\ref{sec:global} ($\beta$=1.59). As in 
$\S$\ref{sec:global}, we also find that the \PLANCK+FIRAS and \PLANCK+DIRBE 
best-fit two-component models from Table \ref{tab:global} outperform single-MBB
alternatives, though only by a relatively small margin. The agreement between 
our correlation slope analysis and the present goodness-of-fit analysis is 
especially encouraging for two main reasons: (1) in the present analysis, dust 
temperature has been allowed to vary on degree scales, whereas in 
$\S$\ref{sec:global} we assumed a single global dust temperature (2) in the
present analysis, our zero-level offsets factor into the dust temperature,
whereas in $\S$6 this was not the case, meaning the former and latter analyses 
agree in spite of their potential to be affected by rather different 
systematics.

@@
